\pkg{Rgbp}: An R Package for Hierarchical Modeling and Method Checking

### 2013-07-22 jss/article.tex
more proof reading

\subsection{Pseudo-data Generation Process}
Figure 1 will be helpful to understand this process. As we can see in (\ref{normalpost}), the distribution of each true parameter ($\mu_{j},~j=1,\ldots, k$) is completely determined by two hyper-parameters, $A$ and $\beta_{(m\times1)}$. So, once we fix these hyper-parameters at specific values, we can generate true parameters. Suppose we sampled 500 $\mathbf{\mu}_{(k\times1)}$'s, \emph{i.e.}, $\{\mathbf{\mu}^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ from the prior distribution in (2), where $A$ and $\beta$ are given. Then, we can also generate $\{\mathbf{y}^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ given each $\mu_{ij},$ where $i$ indicates the $i$-th pseudo-dataset and $j$ does the $j$-th group.

\begin{figure}[h]
\begin{center}
\includegraphics[width=5cm]{process.png}
\caption{Pseudo-data generating process}
\end{center}
\end{figure}

@@

We also need a graphical summary that can give us valuable insight buried in pile of numbers and a function `\code{plot}' is exactly for this purpose.
\begin{CodeChunk}
\begin{CodeInput}
R> plot(p)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.25]{hospital1.png}
\caption{Shrinkage plot and 95\% interval plot}
\end{center}
\end{figure}

The regression towards the mean (RTTM) is obvious in the left-side graph; the observed sample means, empty dots on the upper horizontal line, are shrinking towards the known second-level mean (a blue vertical line at 0.02) to the different extents. Note that some hospitals' ranks have changed by shrinking much harder towards 0.02 than others. For example, the empty square symbol at the crossing point of the two left-most lines (8th and 23rd hospitals on the list above) indicates that seemingly the safest hospital among 31 hospitals in terms of the observed death ratio was not actually safer than seemingly the second safest hospital.

@@

\begin{CodeChunk}
\begin{CodeInput}
R> pcv <- coverage(p, nsim = 10000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h] 
\label{fig:hospital_coverage}
\begin{center}
\includegraphics[width = 5.5cm]{hospital2.png}
\caption{Coverage plot via method checking}
\end{center}
\end{figure}

@@

         obs.mean   se prior.mean shrinkage low.intv post.mean upp.intv post.sd
5           -1.00  9.0      8.168     0.408  -13.297     2.737   16.692   7.634
2            8.00 10.0      8.168     0.459   -7.255     8.077   23.361   7.810
7           18.00 10.0      8.168     0.459   -1.289    13.484   30.821   8.176
4            7.00 11.0      8.168     0.507   -8.780     7.592   23.602   8.257
6            1.00 11.0      8.168     0.507  -13.027     4.633   20.131   8.441
1           28.00 15.0      8.168     0.657   -2.315    14.979   38.763  10.560
3           -3.00 16.0      8.168     0.685  -17.130     4.650   22.477  10.096
8           12.00 18.0      8.168     0.734  -10.208     9.189   29.939  10.227
colMeans     8.75 12.5      8.168     0.552   -9.163     8.168   25.723   8.900
\end{CodeOutput}
\end{CodeChunk}
The output from \code{gbp} provides an easy way to read summary of the results of the estimation. From this there seems to be little evidence that the training provided much of an added benefit with every school's $95\%$ posterior interval containing 0. \pkg{Rgbp} also provides functionality to plot the results of the analysis as seen in \ref{8schoolsplot}.

@@

\begin{figure}[h] \label{8schoolsplot}
\begin{center}
\includegraphics[scale=0.3]{school1.png}
\caption{Shrinkage plot and 95\% interval plot for 8 schools}
\end{center}
\end{figure}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> gcv <- coverage(g, nsim = 10000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h] 
\begin{center}
\includegraphics[width = 5.5cm]{school2.png}
\caption{Coverage plot via method checking for 8 schools}
\end{center}
\label{schoolcoverage}
\end{figure}
%TODO: wrong reference. you mean 'As seen in Figure 5' below?
As seen in \ref{schoolcoverage} the desired $95\%$ coverage probability was achieved for each group in this example.

@@

\begin{CodeChunk}
\begin{CodeInput}
R> plot(b)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.3]{baseball1.png}
\caption{Shrinkage plot and 95\% interval plot}
\end{center}
\end{figure}

@@

The 95\% interval plot shows us range of true batting average for each player, which clarifies the regression toward the mean (RTTM) within two groups. Let's see the 10th, 14th, and 15th players on the graph for example. They are outfielders but their observed batting averages are far lower than the first five outfielders. RTTM means that it can happen by their bad luck though in the long run their batting averages will come back to their expected ones as outfielders (blue horizontal line). So, their posterior means (red dots) can be interpreted as their RTTM.

@@

\begin{CodeChunk}
\begin{CodeInput}
R> bcv <- coverage(b, nsim = 10000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[width = 5.5cm]{baseball2.png}
\caption{Coverage plot via method checking}
\end{center}
\end{figure}

Finally, the estimated average coverage probability is 0.973 based on the Rao-Blackwellization, conservatively satisfying the definition of the 95\% confidence interval.

>>>>

\subsection{Pseudo-data Generation Process}
Figure \ref{fig:pseudo} will be helpful to understand this process. As we can see in (\ref{normalpost}), the distribution of each true parameter ($\mu_{j},~j=1,\ldots, k$) is completely determined by two hyper-parameters, $A$ and $\beta_{(m\times1)}$. So, once we fix these hyper-parameters at specific values, we can generate true parameters. Suppose we sampled 500 $\mathbf{\mu}_{(k\times1)}$'s, \emph{i.e.}, $\{\mathbf{\mu}^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ from the prior distribution in (2), where $A$ and $\beta$ are given. Then, we can also generate $\{\mathbf{y}^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ given each $\mu_{ij},$ where $i$ indicates the $i$-th pseudo-dataset and $j$ does the $j$-th group.

\begin{figure}[h]
\begin{center}
\includegraphics[width=5cm]{process.png}
\caption{Pseudo-data generating process}
\label{fig:pseudo}
\end{center}
\end{figure}

@@

We also need a graphical summary that can give us valuable insight buried in pile of numbers and a function `\code{plot}' is exactly for this purpose.
\begin{CodeChunk}
\begin{CodeInput}
R> plot(p)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.25]{hospital1.png}
\caption{Shrinkage plot and 95\% interval plot}
\label{fig:hospshr}
\end{center}
\end{figure}

In Figure \ref{fig:hospshr} The regression towards the mean (RTTM) is obvious in the left-side graph; the observed sample means, empty dots on the upper horizontal line, are shrinking towards the known second-level mean (a blue vertical line at 0.02) to the different extents. Note that some hospitals' ranks have changed by shrinking much harder towards 0.02 than others. For example, the empty square symbol at the crossing point of the two left-most lines (8th and 23rd hospitals on the list above) indicates that seemingly the safest hospital among 31 hospitals in terms of the observed death ratio was not actually safer than seemingly the second safest hospital.

@@

\begin{CodeChunk}
\begin{CodeInput}
R> pcv <- coverage(p, nsim = 10000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h] 
\begin{center}
\includegraphics[width = 5.5cm]{hospital2.png}
\caption{Coverage plot via method checking}
\label{fig:hospital_coverage}
\end{center}
\end{figure}

@@

         obs.mean   se prior.mean shrinkage low.intv post.mean upp.intv post.sd
5           -1.00  9.0      8.168     0.408  -13.297     2.737   16.692   7.634
2            8.00 10.0      8.168     0.459   -7.255     8.077   23.361   7.810
7           18.00 10.0      8.168     0.459   -1.289    13.484   30.821   8.176
4            7.00 11.0      8.168     0.507   -8.780     7.592   23.602   8.257
6            1.00 11.0      8.168     0.507  -13.027     4.633   20.131   8.441
1           28.00 15.0      8.168     0.657   -2.315    14.979   38.763  10.560
3           -3.00 16.0      8.168     0.685  -17.130     4.650   22.477  10.096
8           12.00 18.0      8.168     0.734  -10.208     9.189   29.939  10.227
colMeans     8.75 12.5      8.168     0.552   -9.163     8.168   25.723   8.900
\end{CodeOutput}
\end{CodeChunk}
The output from \code{gbp} provides an easy way to read summary of the results of the estimation. From this there seems to be little evidence that the training provided much of an added benefit with every school's $95\%$ posterior interval containing 0. \pkg{Rgbp} also provides functionality to plot the results of the analysis as seen in Figure \ref{fig:8schoolsplot}.

@@

\begin{figure}[h] 
\begin{center}
\includegraphics[scale=0.3]{school1.png}
\caption{Shrinkage plot and 95\% interval plot for 8 schools}
\label{fig:8schoolsplot}
\end{center}
\end{figure}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> gcv <- coverage(g, nsim = 10000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h] 
\begin{center}
\includegraphics[width = 5.5cm]{school2.png}
\caption{Coverage plot via method checking for 8 schools}
\label{fig:schoolcoverage}
\end{center}
\end{figure}
%TODO: wrong reference. you mean 'As seen in Figure 5' below?
As seen in Figure \ref{fig:schoolcoverage} the desired $95\%$ coverage probability was achieved for each group in this example.

@@

\begin{CodeChunk}
\begin{CodeInput}
R> plot(b)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.3]{baseball1.png}
\caption{Shrinkage plot and 95\% interval plot}
\label{fig:baseball}
\end{center}
\end{figure}

@@

In Figure \ref{fig:baseball} the 95\% interval plot shows us range of true batting average for each player, which clarifies the regression toward the mean (RTTM) within two groups. Let's see the 10th, 14th, and 15th players on the graph for example. They are outfielders but their observed batting averages are far lower than the first five outfielders. RTTM means that it can happen by their bad luck though in the long run their batting averages will come back to their expected ones as outfielders (blue horizontal line). So, their posterior means (red dots) can be interpreted as their RTTM.

@@

\begin{CodeChunk}
\begin{CodeInput}
R> bcv <- coverage(b, nsim = 10000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[width = 5.5cm]{baseball2.png}
\caption{Coverage plot via method checking}
\label{fig:baseball2}
\end{center}
\end{figure}

Finally, in Figure \ref{fig:baseball2}, we see that the estimated average coverage probability is 0.973 based on the Rao-Blackwellization, conservatively satisfying the definition of the 95\% confidence interval.
